Imputation of incomplete multilevel data

### 2024-02-29 manuscript.qmd
prep case study data

Prerequisites: incomplete dataset and known multilevel modeling strategy (i.e. the most general analytic model to be applied to imputed data).

1. Load the data, make sure the variables are correctly formatted (e.g. numeric clustering variable)
2. Explore the missingness
2. Fix any cluster-level missingness determinately (note that `2l.only` methods do not work if there are inconsistencies, fix those first!)
2. Re-evaluate the missingness
3. Explore bivariate relations and associations with missingness indicators (optionally test the associations?)
4. For each incomplete variable:
  - Determine the imputation method
  - Choose imputation model predictors (see recipe)
5. Set methods vector and predictor matrix
6. Impute the incomplete data
6. If error...
6. After successful run:
  - Evaluate convergence
  - Evaluate imputations
9. Analyze and pool
10. For further multilevel model building, AICs could be pooled, how?

>>>>

Prerequisites: incomplete dataset and known multilevel modeling strategy (i.e. the most general analytic model to be applied to imputed data), plus an assumed missingness mechanism. This tutorial assumes M(C)AR, for MNAR see Munoz et al.

1. Load the data, make sure the variables are correctly formatted (e.g. numeric clustering variable)
2. Explore the missingness
2. Fix any cluster-level missingness determinately (note that `2l.only` methods do not work if there are inconsistencies, fix those first!)
2. Re-evaluate the missingness
3. Explore bivariate relations and associations with missingness indicators (optionally test the associations?)
4. For each incomplete variable:
  - Determine the imputation method
  - Choose imputation model predictors (see recipe)
5. Set methods vector and predictor matrix
6. Impute the incomplete data
6. If error...
6. After successful run:
  - Evaluate convergence
  - Evaluate imputations
9. Analyze and pool
9. If error... (e.g. rescale variables by converting imputations to long format, mutate, then back to mids)
10. For further multilevel model building, AICs could be pooled, how?
